### 2016-04-28 doc/paper/tex/conclusion.tex

\section*{Acknowledgment} 
The funding for this project was provided by ONR N00014-11-1-0027. This work used the Extreme Science and Engineering Discovery Environment (XSEDE), which is supported by National Science Foundation grant number
ACI-1053575. The authors acknowledge the Texas Advanced Computing
Center (TACC) at the University of Texas at Austin for providing HPC resources that have contributed to the research results reported within this paper, URL: http://www.tacc.utexas.edu. We would also like to thank the developer community of PETSc library for their valuable
suggestions during this project.
The third author acknowledges support by the Hausdorff Center for Mathematics
(HCM) at Bonn University,
% and the Transregio 32 research collaborative, both
an initiative funded by the German Research Foundation (DFG).

>>>>

\section*{Acknowledgment} 
The funding for this project was provided by ONR N00014-11-1-0027.
We would also like to thank the technical staff at the Texas Advanced Computing
Center (TACC) and the developer community of PETSc library for their valuable
suggestions during this project.
The third author acknowledges support by the Hausdorff Center for Mathematics
(HCM) at Bonn University,
% and the Transregio 32 research collaborative, both
an initiative funded by the German Research Foundation (DFG).
